### 2018-08-02 paper/introduction.tex
Lemma about refinement and hitting sets added

This paper complements work published by two of the authors
in~\cite{DBLP:conf/pts/CavalcantiS17}. There, fault domains are specified as
collections of processes refining a  ``most general'' fault domain member.
With this concept of fault domains, complete test suites may be finite or
infinite. While this gives important insight into the theory of complete test
suites, we are particularly interested in finite suites when it comes to
their practical application.

Therefore, we present a complementary approach to the definition of CSP fault
domains in this paper. To this end, we observe that every finite-state CSP
process can be semantically represented as a finite normalised transition
graph, whose edges are labelled by the events the process engages in, and
whose nodes are labelled by minimal acceptances or, alternatively, maximal
refusals~\cite{Roscoe:1994:CME:197600}. The maximal refusals  express the
degree of nondeterminism that is present in a given CSP process state that is
in one-one-correspondence to a node of the normalised transition graph.
Inspired by the way that fault-domains are specified for finite state
machines (FSMs), we define them here as the set of CSP processes whose
normalised transition graphs do not exceed the size of the reference model's
graph by more than a give constant.

Our main contributions in this paper are as follows.
%
\begin{enumerate}
\item It is proven that for fault domains of the described type, complete
    test suite generation methods can be given for verifying (1)~trace
    equivalence, (2)~trace refinement, (3)~failures equivalence, and
    (4)~failures refinement.

\item We prove that finite complete test suites can be generated in all
    four cases, when using the fault domains based on the size of the
    members' normalised transition graphs.

\item We present test suite generation techniques for each of the four
    conformance relations by translating algorithms originally elaborated
    for the FSM domain into the CSP world. This translation preserves the
    completeness properties that have previously been established for the
    FSM domain by other authors.
\end{enumerate}
%
The possibility to translate complete test suites between different
formalisms (here FSMs and CSP processes) has been investigated before by two
of the authors~\cite{Huang2017}. \fxwarning{alcc: I miss a paragraph that
discusses what is difficult. So far, it sounds like just application of known
results, which is not true.}

@@

\subsubsection*{Overview}

>>>>

This paper presents complete black-box test suites for divergence-free\footnote{The assumption of divergence freedom is usually applied in black-box testing, since it cannot distinguish between divergence and deadlock.} CSP processes interpreted 
both in the trace   and the failures semantics.  
Our results complement work published by two of the authors
in~\cite{DBLP:conf/pts/CavalcantiS17}. There, fault domains are specified as
collections of processes refining a  ``most general'' fault domain member.
With this concept of fault domains, complete test suites may be finite or
infinite. While this gives important insight into the theory of complete test
suites, we are particularly interested in finite suites when it comes to
their practical application.

Therefore,  a complementary approach to the definition of CSP fault
domains is presented in this paper. To this end, we observe that every finite-state CSP
process can be semantically represented as a finite normalised transition
graph, whose edges are labelled by the events the process engages in, and
whose nodes are labelled by minimal acceptances or, alternatively, maximal
refusals~\cite{Roscoe:1994:CME:197600}. The maximal refusals  express the
degree of nondeterminism that is present in a given CSP process state that is
in one-one-correspondence to a node of the normalised transition graph.
Inspired by the way that fault-domains are specified for finite state
machines, we define them here as the set of CSP processes whose
normalised transition graphs do not exceed the size of the reference model's
graph by more than a give constant.

Our main contributions in this paper consist in the proof that 
for fault domains of the described type, finite, complete
    test suite generation methods can be given for verifying (1)~trace
    equivalence, (2)~trace refinement, (3)~failures equivalence, and
    (4)~failures refinement.

The existence of -- possibly infinite -- complete test suites has been established for process algebras in general and  for CSP in particular by several authors, 
e.g.~\cite{Hennessy:1988:ATP:50497,Schneider:1995:OST:203471.203475,DBLP:conf/fm/PeleskaS96,peleska1997a,DBLP:conf/pts/CavalcantiS17}. To our best knowledge, however, this article is the first to present {\it finite}, complete test suites associated with this class of fault domains.

It should be noted that the presented results are of a theoretical nature: despite being finite, the resulting test suite size will still be too large to be applied in practice to real-world problems.
We discuss a number of promising options how the test suite size can be reduced to become practically applicable.

@@

\subsubsection*{Overview}
In Section~\ref{section:preliminaries}, 
we present the background material relevant to our work.

### 2018-08-02 paper/preliminaries.tex
Lemma about refinement and hitting sets added

In this section, we present the background material relevant to our work.

% =========================================================================
\subsection{Complete Test Suites}
\label{sec:fsmfm}
% =========================================================================

We use the term \emph{signature} to denote a collection of comparable models
represented in an arbitrary formalism. In this article, signatures represent
sets of finite state machines over fixed input and output alphabets, or CSP
processes with finite state, represented by their normalised transition
graphs (see Section~\ref{sec:ntg}).

Given a signature $Sig$  of models, a  \emph{fault model} ${\cal F} =
(M,\le,Dom)$ specifies a \emph{reference model} $M\in Sig$, a
\emph{conformance relation} $\le\ \subseteq Sig\times Sig$ between models,
and a \emph{fault domain} $Dom\subseteq Sig$. This terminology
follows~\cite{gotzhein_fault_1996}, where fault models have been originally
introduced in the context of testing of finite state machines. Note that
fault domains may contain both models conforming to the reference model and
models violating the conformance relation. Note further that the reference
model $M$ is not necessarily a member of the fault domain, although a model
of the SUT behaviour is. For example, $M$ could be nondeterministic, while
only deterministic implementation behaviours might be considered in the fault
domain.
%By $F(Sig,\le)$ we denote the set of all fault models ${\cal F}$
%defined for
%signature $Sig$ and conformance relation $\le$.

Let $\tc(Sig)$ denote the set of all \emph{test cases} applicable to elements
of $Sig$. This abstract notion of test case requires only the existence of a
relation $\pass\subseteq Sig\times \tc(Sig)$. For $(M,U)\in\pass$, the infix
notation $M\ \pass\ U$ is used, and interpreted as {\it `model $M$ passes the
test case $U$'}. If $(M,U)\not\in\pass$ holds, this is abbreviated by $M\
\tfail\ U$. Our specific notion of test cases for CSP models is elaborated in
Section~\ref{sec:csptc}.

A \emph{test suite} $\TS \subseteq \tc(Sig)$ denotes  a set of test cases. A
model $M$ \emph{passes the test suite} $\TS$, also written as $M\ \pass\
\TS$, if, and only if, $M\ \pass\ U$ for all $U\in \TS$. A test suite $\TS$
is called \emph{complete} for fault model ${\cal F} = (M,\le,Dom)$, if, and
only if, the following properties hold.
\begin{enumerate}
\item If a member $M'$ of the fault domain  conforms to the reference model $M$,
it passes the test suite, that is,
$$
\forall M'\in Dom: M'\le M \Rightarrow M'\ \pass\ \TS
$$
This property is usually called \emph{soundness} of the test suite.

\item If a member of the fault domain passes the test suite, it conforms to the reference model, that is,
$$
\forall M'\in Dom: M'\ \pass\ \TS \Rightarrow M'\le M
$$
This property is usually called \emph{exhaustiveness}.
\end{enumerate}
A test suite $\TS$ is \emph{finite} if it contains finitely many test cases and every test
case $U\in\TS$ is finite in the sense that it terminates after a finite number of steps.
It is trivial to see that, if $\TS$ is complete  for   ${\cal F} = (M,\le,Dom)$
and $Dom'\subseteq Dom$, then $\TS$ is also complete for ${\cal F}' = (M,\le,Dom')$.

@@

@@

>>>>

@@

Refinement relations between finite-state CSP processes $P, Q$ 
can be be expressed by means of their normalised transition graphs in the following way.

\begin{lemma}
\label{lemma:tgtrcref}
\begin{eqnarray}
P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
\label{eq:trcrefa}
\\
\label{eq:failrefa}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {}
\\ & & \forall s\in\trc(G(Q)), R_Q\in\maxrefs(G(Q)/s): 
\\ & & \tabd
\exists R_P\in\maxrefs(G(P)/s): R_Q\subseteq R_P
\\
\label{eq:failrefb}
P \lessdet_F Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P)) \wedge {}
\\ & & \forall s\in\trc(G(Q)), A_Q\in\minaccs(G(Q)/s):
\\ & & \tabd
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\end{eqnarray}
\end{lemma}

@@

% =========================================================================
\subsection{Test Cases and Complete Test Suites}
\label{sec:cspcompletedef}
% =========================================================================

@todo

% =========================================================================
\subsection{Minimal Hitting Sets}
\label{sec:hit}
% =========================================================================

When testing for failures refinement, it will become apparent that the main idea of the underlying test strategy can be based on solving a \emph{hitting set problem}. Given a collection of finite sets $C = \{ A_1,\dots,A_n\}$ that are each subsets of a universe $\Sigma$, a \emph{hitting set} $H\subseteq\Sigma$ is a set satisfying
\begin{equation}
\label{eq:hit}
\forall A\in C: H\cap C \neq\varnothing.
\end{equation}

A \emph{minimal hitting set} is a hitting set which cannot be further reduced without losing 
the characteristinc property (\ref{eq:hit}). The problem of determining minimal hitting sets is known to be NP-hard~\cite{Book1975-BOOKRM}, but we will see below that it reduces 
the effort of testing for failures refinement from a factor of $2^\Sigma$ to a factor that equals the number of minimal hitting sets.

For testing in the failures model, the following lemmas about hitting sets are required.

\begin{lemma}
\label{lemma:hseta}
Let $P, Q$ be two finite-state CSP processes satisfying $P\lessdet_T Q$. 
For each $s\in\trc(P)$,
let $\text{MINHIT}(s)$ denote the
collection of all minimal hitting sets of $\minaccs(P/s)$. 
Then the following statements are equivalent.
\begin{enumerate}
\item $P\lessdet_F Q$
\item For all $s\in\trc(P)\cap \trc(Q)$ and $H \in  \text{MINHIT}(s)$, $H$ is
a (not necessariliy minimal) hitting set of $\minaccs(Q/s)$.
\end{enumerate}
\end{lemma}
\begin{proof}
For showing ``$1 \Rightarrow 2$'', assume that $P\lessdet_F Q$ and suppose that
$s\in\trc(P)\cap \trc(Q)$. Then Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), implies that 
\[
\forall A_Q\in\minaccs(G(Q)/s):
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\]
Therefore, every minimal acceptance set $A_Q\in\minaccs(G(Q)/s)$ contains a
minimal acceptance set from  \minaccs(G(P)/s). As a consequence, any hitting set
$H \in  \text{MINHIT}(s)$ also has a non-empty intersection with every 
$A_Q\in\minaccs(G(Q)/s)$.

To prove ``$2 \Rightarrow 1$'',
assume $P\lessdet_T Q$, but $P\not\lessdet_F Q$. According to Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), there exists $s\in\trc(P)\cap \trc(Q)$ such that 
\[
\exists A_Q\in\minaccs(G(Q)/s): \forall A_P\in\minaccs(G(P)/s): A_P\not\subseteq A_Q (*)
\]
Define 
\[
\overline H = \bigcup_{A_P\in\minaccs(G(P)/s)} \big( A_P \setminus A_Q \big).
\]
Since $A_P \setminus A_Q \neq\varnothing$ because of (*), $\overline H$ is a hitting set
of $\minaccs(G(P)/s)$ which has a non-empty intersection with $A_Q$. Minimising 
$\overline H$ induces the existence
of a minimal hitting set $H\in \text{MINHIT}(s)$ which is {\it not} a hitting set of 
of $\minaccs(G(Q)/s)$. This completes the proof of the lemma.
\xbox
\end{proof}

%\begin{lemma}
%\label{lemma:hsetb}
%
%\end{lemma}
%\begin{proof}
%asd
%\end{proof}
%
